\documentclass[11pt]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{enumitem} % for [leftmargin=*]
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Abhishek}{Raut}{ 
\href{http://linkedin.com/in/abhishek-raut-736a3a21a}{LinkedIn} | 
\href{mailto:iamabhishekraut01@gmail.com}{iamabhishekraut01@gmail.com} | 
+91-9665704204 | Pune, Maharashtra
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROFESSIONAL SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Professional Summary}
Motivated IT graduate with experience in full-stack development, aerospace manufacturing, and UI/UX design. Skilled in JavaScript, Java, React.js, and modern web technologies. Strong problem-solving skills with a record of improving workflows and delivering responsive projects.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{Pune University}
\descript{BE in Information Technology}
\location{July 2025 | Pune, Maharashtra}
\sectionsep

\subsection{MSBTE}
\descript{Diploma in Mechanical Engg.}
\location{May 2021 | Karad, Maharashtra}
Government Polytechnic Karad \\
\location{Grade: First Class with Distinction | Percentage: 85.38}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
\href{https://github.com/raut-abhishek}{GitHub: raut-abhishek} \\
\href{https://linkedin.com/in/abhishek-raut-736a3a21a}{LinkedIn: abhishek-raut}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
Data Structures and Algorithms \\
Object-Oriented Programming \\
Database Management Systems \\
Computer Networks \\
Operating Systems \\
Software Engineering \\
Blockchain Technology \\
Web Technologies \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Proficient}
JavaScript (ES6+), HTML5, CSS3, Java, Git, GitHub

\subsection{Familiar}
React.js, Tailwind CSS, GSAP, Shery.js, Blockchain Basics, Distributed Systems, REST APIs

\subsection{Core Concepts}
Object-Oriented Programming (OOP), Asynchronous JavaScript
\sectionsep

\end{minipage} 
\hspace{0.05\textwidth} % fixed gap between columns
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.61\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\runsubsection{Personal Portfolio Website}
\descript{}
\location{Frontend Development | HTML, CSS, GSAP, Shery.js}
\begin{itemize}[leftmargin=*]
\item Designed and developed a responsive personal portfolio showcasing projects and skills.
\item Implemented smooth animations and interactive UI using GSAP and Shery.js.
\item Applied modern CSS techniques for visually appealing layout.
\end{itemize}
\sectionsep

\runsubsection{Local Full-Stack Project}
\descript{}
\location{Collaboration with Peers | Frontend: HTML, CSS, JavaScript | Backend: Node.js, MongoDB}
\begin{itemize}[leftmargin=*]
\item Contributed to frontend interface design and integrated backend APIs.
\item Improved understanding of full-stack development workflow.
\end{itemize}
\sectionsep

\runsubsection{Additional Learning Projects}
\descript{}
\begin{itemize}[leftmargin=*]
\item Gradient & UI Design Experiments - Created custom gradients (Iced Moondust, Velvet Petrol) and responsive layouts.
\item JavaScript Asynchronous Demos - Built interactive examples for callbacks, promises, and async/await.
\item TailwindCSS UI Components - Developed reusable UI components with animations and modern layouts.
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience} 
\runsubsection{GE Aerospace Multimodal Manufacturing Facility (MMF)}
\descript{Aerospace Apprentice – Quality \& Production}
\location{Sept 2021 – Nov 2022 | Pune, Maharashtra}
\begin{itemize}[leftmargin=*]
    \item Executed \textbf{First Article Inspections (FAI)} ensuring compliance with \textbf{AS9100 aerospace quality standards}.
    \item Operated \textbf{TRUMPF Trulaser} and \textbf{CMM Arm} for precision aerospace component inspection.
    \item Implemented \textbf{Lean practices} and \textbf{5S methodology}, earning internal recognition.
    \item Designed a \textbf{pneumatic ball-rail bed} reducing fixture loading/unloading time by \textbf{50\%} and downtime by \textbf{20\%}.
    \item Initiated multiple \textbf{Kaizens} to improve workflow efficiency.
    \item Raised and documented \textbf{safety/non-compliance concerns}, preventing unsafe workplace activities.
    \item Led cross-functional team in workplace decoration competition - achieved 1st place.
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATIONS (Optional)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Publications}
%\renewcommand\refname{\vskip -1.5em}
%\bibliographystyle{abbrv}
%\nocite{*}

\end{minipage} 
\end{document}
